Building socket-aware BPF programs

### 2018-10-29 paper/paper.tex
paper: Turn linux version into a command

\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\lstinputlisting[float=*b,%
  caption={BPF API structures for socket lookup (Linux v4.20)},%
  language=c,%
  label=lst:helper-struct,%
  breaklines=true]{sk-lookup-structures.h}

>>>>

\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}
\newcommand\linuxversion{v4.20}

@@

\lstinputlisting[float=*b,%
  caption={BPF API structures for socket lookup (Linux~\linuxversion)},%
  language=c,%
  label=lst:helper-struct,%
  breaklines=true]{sk-lookup-structures.h}
